Open Policing Project Tutorial

### 2019-02-28 nicar_tutorial.Rmd
progress

# Compute sunset time for each date in our dataset
sunset_times <- 
  stops %>%
  mutate(
    lat = center_lat,
    lon = center_lng
  ) %>% 
  select(date, lat, lon) %>%
  distinct() %>%
  mutate(
    sunset = format(
      getSunlightTimes(data = ., keep = c("sunset"), tz = tz)$sunset,
      "%H:%M:%S"
    ), 
    sunset_minute = time_to_minute(sunset)
  ) %>% 
  select(date, sunset, sunset_minute)

vod_stops <- 
  stops %>% 
  left_join(
    sunset_times,
    by = "date"
  ) %>% 
  mutate(
    minute = time_to_minute(time),
    minutes_after_sunset = minute - sunset_minute,
    is_dark = minute > sunset_minute,
    min_sunset_minute = min(sunset_minute),
    max_sunset_minute = max(sunset_minute),
    is_black = subject_race == "black"
  ) %>% 
  filter(
    # NOTE: filter to get only the intertwilight period
    minute >= min_sunset_minute,
    minute <= max_sunset_minute,
    subject_race %in% c("black", "white")
  )
```

@@

summary(mod)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
exp(summary(mod)$coefficients["is_darkTRUE", "Estimate"])
exp(confint(mod, parm = "is_darkTRUE"))
```

@@

summary(mod)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
# confint(mod, parm = "is_darkTRUE")
```

>>>>

# Compute sunset time for each date in our dataset
sunset_times <- 
  stops %>%
  mutate(
    lat = center_lat,
    lon = center_lng
  ) %>% 
  select(date, lat, lon) %>%
  distinct() %>%
  getSunlightTimes(
    data = ., 
    keep = c("sunset", "dusk"), 
    tz = tz
  ) %>% 
  mutate_at(vars("sunset", "dusk"), ~format(., "%H:%M:%S")) %>% 
  mutate(
    sunset_minute = time_to_minute(sunset),
    dusk_minute = time_to_minute(dusk),
    date = ymd(str_sub(date, 1, 10))
  ) %>% 
  select(date, sunset, dusk, ends_with("minute"))

vod_stops <- 
  stops %>% 
  left_join(
    sunset_times,
    by = "date"
  ) %>% 
  mutate(
    minute = time_to_minute(time),
    minutes_after_sunset = minute - sunset_minute,
    is_dark = minute > sunset_minute,
    min_sunset_minute = min(sunset_minute),
    max_sunset_minute = max(sunset_minute),
    is_black = subject_race == "black"
  ) %>% 
  filter(
    # NOTE: filter to get only the intertwilight period
    minute >= min_sunset_minute,
    minute <= max_sunset_minute,
    !(minute > sunset_minute & minute < dusk_minute),
    subject_race %in% c("black", "white")
  )
```

@@

summary(mod)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
exp(summary(mod)$coefficients["is_darkTRUE", "Estimate"])
```

@@

summary(mod)$coefficients["is_darkTRUE", c("Estimate", "Std. Error")]
exp(summary(mod)$coefficients["is_darkTRUE", "Estimate"])
```
